Open Science, Open Plant Pathology

### 2020-05-18 analysis/paper/paper.Rmd
Correct Excel rank in text
Replace gsheet with googlesheets4 to simplify package usage

The use of programming or scripting languages such as R, SAS or Python enable you as a scientist to keep very detailed records of what was computationally performed.
This is as opposed to using software such as spreadsheet programs like Excel, gsheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.

@@

In order for us to determine where we are as a discipline with regards to sharing openly and reproducible papers and data, we randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
Three hundred articles were randomly selected from issues published from 2012 to 2018.
A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
The pages list was numbered from page one and went to page 150.
This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
The list of journals was saved from Google's gsheets as a comma separated value (CSV) file for later use and distribution in a research compendium.

@@

The most frequently cited software was SAS.
The remainder were mostly specialised softwares with the exception of Microsoft Excel, tied for 8th.

>>>>

The use of programming or scripting languages such as R, SAS or Python enable you as a scientist to keep very detailed records of what was computationally performed.
This is as opposed to using software such as spreadsheet programs like Excel, Google sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization (but should not be) or other point-and-click software packages that do not enable you to keep an accurate record of the steps taken to import, format, visualise and analyse data.

@@

In order for us to determine where we are as a discipline with regards to sharing openly and reproducible papers and data, we randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
Three hundred articles were randomly selected from issues published from 2012 to 2018.
A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
The pages list was numbered from page one and went to page 150.
This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
The list of journals was saved from Google's sheets as a comma separated value (CSV) file for later use and distribution in a research compendium.

@@

The most frequently cited software was SAS.
The remainder were mostly specialised softwares with the exception of Microsoft Excel, tied for 9th.
